### 2014-09-25 fundamentals/examples.tex
more content and comments added in intro, examples, impl, and verification
adds some basic stuff to the ecosystem examples section.

Current and past simulations with the Cyclus simulator have already 
demonstrated a range of uses.

@@

External modules have been (cite cyder, separations, streamblender, demandinst, 
commodconverter, etc.) and are being (cite brightlight, UTK module, etc.) 
developed for contribution to the cyclus ecosystem of models.

@@

>>>>

@@

The archetypes created by user-developers 
and the archetypes provided in the \Cycamore repository of additional modules 
together form an `ecosystem' of capabilities. Since the long term vision for 
the \Cyclus framework includes an ever-expanding ecosystem of both general and 
specialized capability extensions within that ecosytem. The early growth and 
cross-institutional contributions to this ecosystem demonstrates a significant 
acheivement by the \Cyclus framework.

\subsubsection{The Cyclus Additional Modules Repository}

\Cycamore, the \Cyclus additional modules repository, provides a fundamental 
set of agent archetypes for basic simulation functionality within \Cyclus.
Since the \Cyclus framework relies on external archetypes to represent the 
agents within a simulation, 
\Cycamore provides the basic archetypes a new user needs to get started running 
simple simulations. 
These archetypes support a minimal set of fuel cycle simulation goals and 
provide, by example, a guide to new developers who would seek to contribute 
their own archetypes outside of \Cycamore.

\subsubsection{External Modules}
External modules have been 
\cite{cyder,separations,streamblender,mktdriveninst,commodconverter} and are 
being \cite{britelite,utk} developed for contribution to the cyclus ecosystem 
of models.

@@

% MJG - INPRO should be tried again. @rwcarlsen has been running lots of
% simulations with the batch reactor, and its the second generation of my
% reactor models. We could easily use the same demand schedule and enrichment
% facility parameters and run it again.
